GPU-based Adaptive Beamforming for Active Sonar Imaging

### 2012-06-26 ECUA2012/gpu_capon_ecua2012.tex

\author{%
\begin{tabular}{p{45mm}p{125mm}}
Jo~Inge~Buskenes & Department of Informatics, University of Oslo, Norway \\
Jon~Petter~Aasen & Mi Lab, Norwegian University of Science and Technology, Norway \\
Carl-Inge~Colombo~Nilsen & Department of Informatics, University of Oslo, Norway \\
Andreas-Austeng & Department of Informatics, University of Oslo, Norway
\end{tabular}
}

>>>>

\author{%
\begin{tabular}{p{45mm}p{125mm}}
Jo~Inge~Buskenes & Department of Informatics, University of Oslo, Norway \\
Jon~Petter~Aasen & Mi Lab, Norwegian University of Science and Technology, Norway \\
Carl-Inge~Colombo~Nilsen & Department of Informatics, University of Oslo, Norway \\
Andreas~Austeng & Department of Informatics, University of Oslo, Norway
\end{tabular}
}
